Papers

### 2023-11-30 quarto/index.qmd
update

*If you are interested in <font color="#ff0000">research internship</font> on large language models at the Llama team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*

>>>>

*If you are interested in <font color="#ff0000">research internship</font> on large language models with our team in 2024, feel free to <a href="img/email.png" target="_blank">email me</a>.*
